Using WordNet and Short-Term Memory for Contextual Disambiguation

### 2017-04-25 Draft_2.tex
Changed Title

        \Huge
        \textbf{Using WordNet and a Short-Term Memory model for Semantic Analysis}
        \vspace{2cm}

@@

        \Large
        Wordcount - 11723\\
        \small
        (Wordcount produced using wc - w, \\
        this includes all the body of the report,\\
         and Appendix A)\\
        \large
        \vspace{0.8cm}
        Supervisor - Dr Dimitar Kazakov\\
        Department of Computer Science\\
        University of York\\
        20 November 2016

@@

\subsubsection{Short-term Memory}
\label{ShortTerm}
The short-term memory (STM) is a structure of finite capacity, used to store items for periods usually of no more than 15-30 seconds \cite{MemoryBaddeleyEysenkAnderson}. In 1955, G. Miller, based upon previous experimental results, concluded that the finite size of the STM existed in the realm of 7$\pm$2 items of information \cite{SevenPlusMinusTwo}.

@@

\begin{figure}[h]
	\includegraphics[scale=0.5]{gantt.png}
	\caption{Gantt chart showing plan for implementation}
	\label{fig:gantt}
\end{figure}

@@

\begin{table}
\begin{center}
\begin{tabular}{|p{8em}|p{8em}|p{8em}|}
	\hline
	STM size & Accuracy (\%) & Directly Seen (\%) \\
	\hline
	5 & 47 & 48\\
	\hline
	6 & 47 & 51\\
	\hline
	7 & 46 & 54\\
	\hline
	8 & 46 & 55\\
	\hline
	9 & 46 & 58\\
	\hline
\end{tabular}
\end{center}
\caption{The effect of STM size on system performance}
\label{table:STMSize}
\end{table}

@@

\begin{table}
\begin{center}
\begin{tabular}{|p{2em}|p{7em}|p{7em}|}
	\hline
	a & Accuracy (\%) & Directly Seen (\%) \\
	\hline
	1 & 45 & 40\\
	\hline
	2 & 46 & 39\\
	\hline
	3 & 45 & 44\\
	\hline
	4 & 46 & 40\\
	\hline
	5 & 43 & 40\\
	\hline
\end{tabular}
\end{center}
\caption{The effect of changing $a$ on system performance}
\label{table:aActivation}
\end{table}

@@

\begin{table}
\begin{center}
\begin{tabular}{|p{2em}|p{7em}|p{7em}|}
	\hline
	b & Accuracy (\%) & Directly Seen (\%) \\
	\hline
	1 & 46 & 39\\
	\hline
	$\frac{1}{2}$ & 47 & 45\\
	\hline
	$\frac{1}{4}$ & 46 & 51\\
	\hline
	$\frac{1}{8}$ & 47 & 52\\
	\hline
	$\frac{1}{16}$ & 46 & 52\\
	\hline
\end{tabular}
\end{center}
\caption{The effect of changing $b$ on system performance}
\label{table:bActivation}
\end{table}

@@

\begin{table}
\begin{center}
\begin{tabular}{|p{2em}|p{7em}|p{7em}|}
	\hline
	Boost & Accuracy (\%) & Directly Seen (\%) \\
	\hline
	0 & 46 & 39\\
	\hline
	0.5 & 48 & 35\\
	\hline
	1 & 51 & 21\\
	\hline
	1.5 & 51 & 19\\
	\hline
	2 & 51 & 22\\
	\hline
\end{tabular}
\end{center}
\caption{The effect of changing the episodic buffer boost on system performance}
\label{table:EBboost}
\end{table}

@@

\begin{table}
\begin{center}
\begin{tabular}{|p{7em}|p{7em}|p{7em}|}
	\hline
	Algorithm & Accuracy (\%) & Directly Seen (\%) \\
	\hline
	Hyponym & 51 & 19\\
	\hline
	Hypernym & 50 & 19\\
	\hline
\end{tabular}
\end{center}
\caption{The effect of changing the disambiguation algorithm on system performance}
\label{table:Algorithm}
\end{table}

@@

\begin{table}
\begin{center}
\begin{tabular}{|p{2em}|p{7em}|p{7em}|}
	\hline
	Delay & Accuracy (\%) & Directly Seen (\%) \\
	\hline
	0 & 51 & 19\\
	\hline
	1 & 53 & 13\\
	\hline
	2 & 53 & 12\\
	\hline
\end{tabular}
\end{center}
\caption{The effect of changing the disambiguation delay on system performance}
\label{table:Delay}
\end{table}

@@

\begin{table}
\begin{center}
\begin{tabular}{|p{5em}|p{7em}|p{7em}|}
	\hline
	Sanity Check & Accuracy (\%) & Directly Seen (\%) \\
	\hline
	On & 53 & 12\\
	\hline
	Off & 50 & 11\\
	\hline
\end{tabular}
\end{center}
\caption{The effect of sanity checks on system performance}
\label{table:Sanity}
\end{table}

>>>>

        \Huge
        \textbf{Using WordNet and the Working Memory Model for Semantic Analysis}
        \vspace{2cm}

@@

        \Large
        Wordcount - 11799\\
        \small
        (Wordcount produced using wc - w, \\
        this includes all the body of the report,\\
         and Appendix A)\\
        \large
        \vspace{0.8cm}
        Supervisor - Dr Dimitar Kazakov\\
        Department of Computer Science\\
        University of York\\
        25 April 2017

@@

\subsubsection{Short-term Memory}
\label{ShortTerm}
The short-term memory (STM) is a structure of finite capacity, used to store items for periods usually of no more than 15-30 seconds \cite{MemoryBaddeleyEysenkAnderson}. In 1956, G. Miller, based upon previous experimental results, concluded that the finite size of the STM existed in the realm of 7$\pm$2 items of information \cite{SevenPlusMinusTwo}.

@@

\begin{figure}[h]
	\includegraphics[scale=0.5]{gantt.png}
	\caption{GANTT CHART SHOWING PLAN FOR IMPLEMENTATION}
	\label{fig:gantt}
\end{figure}

@@

\begin{table}
\begin{center}
\begin{tabular}{|p{8em}|p{8em}|p{8em}|}
	\hline
	STM size & Accuracy (\%) & Directly Seen (\%) \\
	\hline
	5 & 47 & 48\\
	\hline
	6 & 47 & 51\\
	\hline
	7 & 46 & 54\\
	\hline
	8 & 46 & 55\\
	\hline
	9 & 46 & 58\\
	\hline
\end{tabular}
\end{center}
\caption{THE EFFECT OF STM SIZE ON SYSTEM PERFORMANCE}
\label{table:STMSize}
\end{table}

@@

\begin{table}
\begin{center}
\begin{tabular}{|p{2em}|p{7em}|p{7em}|}
	\hline
	a & Accuracy (\%) & Directly Seen (\%) \\
	\hline
	1 & 45 & 40\\
	\hline
	2 & 46 & 39\\
	\hline
	3 & 45 & 44\\
	\hline
	4 & 46 & 40\\
	\hline
	5 & 43 & 40\\
	\hline
\end{tabular}
\end{center}
\caption{THE EFFECT OF CHANGING $a$ ON SYSTEM PERFORMANCE}
\label{table:aActivation}
\end{table}

@@

\begin{table}
\begin{center}
\begin{tabular}{|p{2em}|p{7em}|p{7em}|}
	\hline
	b & Accuracy (\%) & Directly Seen (\%) \\
	\hline
	1 & 46 & 39\\
	\hline
	$\frac{1}{2}$ & 47 & 45\\
	\hline
	$\frac{1}{4}$ & 46 & 51\\
	\hline
	$\frac{1}{8}$ & 47 & 52\\
	\hline
	$\frac{1}{16}$ & 46 & 52\\
	\hline
\end{tabular}
\end{center}
\caption{THE EFFECT OF CHANGING $b$ ON SYSTEM PERFORMANCE}
\label{table:bActivation}
\end{table}

@@

\begin{table}
\begin{center}
\begin{tabular}{|p{2em}|p{7em}|p{7em}|}
	\hline
	Boost & Accuracy (\%) & Directly Seen (\%) \\
	\hline
	0 & 46 & 39\\
	\hline
	0.5 & 48 & 35\\
	\hline
	1 & 51 & 21\\
	\hline
	1.5 & 51 & 19\\
	\hline
	2 & 51 & 22\\
	\hline
\end{tabular}
\end{center}
\caption{THE EFFECT OF CHANGING THE EPISODIC BUFFER BOOST ON SYSTEM PERFORMANCE}
\label{table:EBboost}
\end{table}

@@

\begin{table}
\begin{center}
\begin{tabular}{|p{7em}|p{7em}|p{7em}|}
	\hline
	Algorithm & Accuracy (\%) & Directly Seen (\%) \\
	\hline
	Hyponym & 51 & 19\\
	\hline
	Hypernym & 50 & 19\\
	\hline
\end{tabular}
\end{center}
\caption{THE EFFECT OF CHANGING THE DISAMBIGUATION ALGORITHM ON SYSTEM PERFORMANCE}
\label{table:Algorithm}
\end{table}

@@

\begin{table}
\begin{center}
\begin{tabular}{|p{2em}|p{7em}|p{7em}|}
	\hline
	Delay & Accuracy (\%) & Directly Seen (\%) \\
	\hline
	0 & 51 & 19\\
	\hline
	1 & 53 & 13\\
	\hline
	2 & 53 & 12\\
	\hline
\end{tabular}
\end{center}
\caption{THE EFFECT OF CHANGING THE DISAMBIGUATION DELAY ON SYSTEM PERFORMANCE}
\label{table:Delay}
\end{table}

@@

\begin{table}
\begin{center}
\begin{tabular}{|p{5em}|p{7em}|p{7em}|}
	\hline
	Sanity Check & Accuracy (\%) & Directly Seen (\%) \\
	\hline
	On & 53 & 12\\
	\hline
	Off & 50 & 11\\
	\hline
\end{tabular}
\end{center}
\caption{THE EFFECT OF SANITY CHECKS ON SYSTEM PERFORMANCE}
\label{table:Sanity}
\end{table}
